Exploring Local Explanations of Non-linear Models Using Animated Linear Projections

### 2022-01-13 _paper.tex

The initial frame is the normalized SHAP values of the PI. The current projection basis is depicted as the width of a bar, the feature's contribution to the horizontal axis. The normalized values of all instances are shown as vertical parallel coordinate plots.

@@

{\centering \includegraphics[width=1\linewidth]{./figures/app_classification}

>>>>

The initial frame is the normalized SHAP values of the PI. The distribution normalized values from all instances are shown depicted in the basis as vertical parallel coordinate plots, where each line connects an instance's feature attribution. The PI is highlighted as larger dashed line and CI as a dotted line. The current projection basis is depicted as the width of a bar, the feature contributions to the horizontal axis.

@@

{\centering \includegraphics[width=1\linewidth]{./figures/app_classification_annotations}
